Boosting

### 2021-12-07 boosting.Rmd
Added Boosting importance

@@

```{r}
boost <- gbm(HeartDisease~.,data=train,n.trees=1000,shrinkage=0.01,interaction.depth = 1 ,distribution = "bernoulli")

boostpred = ifelse(predict(boost,test, n.trees = 2000, "response") > 0.5, 
                             "1", "0")

@@

>>>>

set.seed(445)

@@

```{r}
boost <- gbm(HeartDisease~.,data=train,n.trees=500,shrinkage=0.01,interaction.depth = 1 ,distribution = "bernoulli")

boostpred = ifelse(predict(boost,test, n.trees = 500, "response") > 0.5, 
                             "1", "0")

@@

summary(boost)
